Relationships in the extremes and their influence on competition and coexistence: Supporting information

### 2022-03-10 paper/SupMat.Rnw
some changes to sup mat, mainly

%***DAN: Jasmin, please start on this section when you get a chance. Here are some topics that need
%to be covered:
Estimations of $Q_i(t)$, $V_i(t)$, and $K_i(t)$, temperature dependence functions for 
cell quota, reproduction rate, and half saturation, respectively, were used to 
paramaterize the competing diatom model outlined in the paper. 
Values of and subsequent function estimations are plotted in Figure \ref{fig:VQK}. 
\cite{Descamps_2005} obtained estimated values for $Q_i$, $V_i$, and $K_i$ from 
single species nine-day batch experiments at four different temperatures ($6^\circ$C, 
$12^\circ$C, $18^\circ$C, $24^\circ$C) (see Table 1 of \cite{Descamps_2005}) and further
computed linear interpolations to
functions $Q_i(t)$, $V_i(t)$, and $K_i(t)$. These values and functions are 
indicated in Figure \ref{fig:VKQ} by open circles and dashed lines. 
\cite{Ellner_2016, Ellner_2019} used slightly modified values and functions,
indicated in \ref{fig:VQK} by filled circles and solid lines. 
Our investigation follows that of \cite{Ellner_2016, Ellner_2019} and 
uses the modified functions of  $Q_i(t)$, $V_i(t)$, and $K_i(t)$ to analyze coexistence.

%be very clear here. To give one example of the need for care, here, Ellner et al (2019) state on p. 6
%of their paper that K_1 and K_2 were constant for the range of temperature considered, and they state
%that they took constant values for these things. However, we used a larger range of temperatures. 
%Depending on which of K1fun/K2fun versus K1flatfun/K2flatfun (from DDataAndVKQfuns.R) was actually used
%may make a difference, so we have to specify. Note that even K1flatfun/K2flatfun were not actually flat
%for the whole temperature range 6-24 degrees C, though they were for the range of temperature Ellner
%et al considered. We should not say we used flat K1 and K2 functions unless we are sure we only ever
%used temperatures in the flat ranges of these functions. Better just to describe the functions we
%actually used, where the best way to describe them *may* be by plotting them. Anyway, what you need to
%do is make sure you know what versions of each of these 6 functions your code actually used, and then
%describe the functions precisely in this section.

@@

Our decomposition is defined by $E(t)=\theta(t)$, 
$C_{i \bs i}(t)=(K_i(t)+S(t))/S(t)$ and $r_i(E_i,C_{i \bs i})=\frac{V_i(E)}{C_{i \bs i}} -D$. 
We note that our definition and selection of our "features" of interest are
options among many and features need not be limited to $E$ and $C$ \citep{Ellner_2019}. 
For example \cite{Ellner_2019} decomposes coexistence with respect to fluctuation in
inflow silicate concentration, $S$, and temperature, and \cite{Ellner_2016} decomposes
coexistence using classical $E$ and $C$ drivers, but define $E=V(t)$. 
Like \cite{Ellner_2016}, we set $C_{i \bs i}(t)=(K_i(t)+S(t))/S(t)$ to reflect 
potential versus actual growth of the diatom populations. 
Choice of drivers and their definitions are up to the investigator,
but should refelct real variables that influence population growth.

@@

\begin{figure}
\includegraphics[width=.66\textwidth]{../results_figs/VKQfig.pdf}
\caption[Species growth rate, silica uptake, and half sturation responses to changes in temperature.]
{Species maximum growth rate (a), half saturation constant (b), and silica uptake (c) responses to changes in temperature. Species 1 is \emph{F. crotonensis}, shown in blue, and species 2 is \emph{C. pseudostelligera}, shown in red. Open circles and dashed lines indicate estimated data and interpolations from \cite{Descamps_2005} and closed circles and solid lines indicate values and function used in our analysis as defined in \cite{Ellner_2016, Ellner_2019}. \label{fig:VKQ}}
\end{figure}

>>>>

Estimates of the temperature dependence functions $Q_i(t)$, $V_i(t)$, and $K_i(t)$, 
produced by earlier authors \cite{Descamps_2005,Ellner_2016,Ellner_2019} and which are part of the parameterization
of the diatom competition model described in the main text, are now described.
\cite{Descamps_2005} estimated values for $Q_i(t)$, $V_i(t)$, and $K_i(t)$ from 
single-species, nine-day batch experiments at four different temperatures ($6^\circ$C, 
$12^\circ$C, $18^\circ$C, $24^\circ$C) (see Table 1 of \cite{Descamps_2005}) and 
used linear interpolations for the
functions $Q_i(t)$, $V_i(t)$, and $K_i(t)$. Their values and functions are 
pictured in Fig. \ref{fig:VKQ} using open circles and dashed lines.
\cite{Ellner_2016, Ellner_2019} used slightly modified values and functions,
pictured in Fig. \ref{fig:VKQ} by filled circles and solid lines. 
Our investigation follows \cite{Ellner_2016, Ellner_2019} and 
uses their modified functions.

@@

Our decomposition of GWR is defined by the choices $E(t)=\theta(t)$, 
$C_{i \bs i}(t)=(K_i(t)+S(t))/S(t)$ and $r_i(E_i,C_{i \bs i})=\frac{V_i(E)}{C_{i \bs i}} -D$. 
Other choices are possible. For instance, \cite{Ellner_2016} also considers

We note that our definition and selection of our "features" of interest are
options among many and features need not be limited to $E$ and $C$ \citep{Ellner_2019}. 
For example \cite{Ellner_2019} decomposes coexistence with respect to fluctuation in
inflow silicate concentration, $S$, and temperature, and \cite{Ellner_2016} decomposes
coexistence using classical $E$ and $C$ drivers, but define $E=V(t)$.

Like \cite{Ellner_2016}, we set $C_{i \bs i}(t)=(K_i(t)+S(t))/S(t)$ to reflect 
potential versus actual growth of the diatom populations.

@@

\begin{figure}
\includegraphics[width=.66\textwidth]{../results_figs/VKQfig.pdf}
\caption[Maximum growth rate, cellular silicate content, and half sturation constant dependences on temperature.]
{Species maximum population growth rates, $V_i$ (a), half saturation constants for the dependence 
of growth rates on nutrient concentration, $K_i$ (b), and cellular silicate content, $Q_i$ (c) dependend on 
temperature in ways explored by \cite{Descamps_2005} and \cite{Ellner_2016, Ellner_2019} and 
pictured here. Species 1 is \emph{F. crotonensis}, shown in blue, and species 2 is 
\emph{C. pseudostelligera}, shown in red. Open circles and dashed lines indicate estimated 
values and interpolations from \cite{Descamps_2005} and closed circles and solid lines indicate 
values and functions used by \cite{Ellner_2016, Ellner_2019} and in our analyses. The two sets of
estimates and functions coincide on (c).\label{fig:VKQ}}
\end{figure}
%***DAN: I added the last sentence indicating the two sets of data and functions coincide on (c), can you please
%check that and let me know if it's true, Jasmin?
